Study of Higgs to WW Coupling Measurement Performance through $e^+e^-\rig\nu\bar{\nu} b\bar{b}$ at Future Circular Colider - Electron Positron

### 2016-08-02 H_WW_Coupling/tex/paper.tex
introduction revision and migration

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{amsmath,amssymb}
% \usepackage{feynmp}
\usepackage{url}
\usepackage{ulem}
\usepackage{multirow}
\usepackage{hyperref,color}
\renewcommand{\sfdefault}{phv}
\renewcommand{\baselinestretch}{1.2}

@@

% \usepackage{booktabs,siunitx}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{ragged2e}
\newcolumntype{Y}{>{\centering\arraybackslash}X}

% \AtBeginDocument{
% % \heavyrulewidth=.08em
% \lightrulewidth=.05em
% \cmidrulewidth=.03em
% \belowrulesep=.65ex
% \belowbottomsep=0pt
% \aboverulesep=.4ex
% \abovetopsep=0pt
% \cmidrulesep=\doublerulesep
% \cmidrulekern=.5em
% \defaultaddspace=.5em
% }

@@

\begin{abstract}
This investigation seeks to evaluate the potential performance capabilities of the measurment of Higgs to WW coupling at the FCCee - a future $e^+e^-$ collider. The signal process used in the investigation is $e^+e^-\rig\nu\bar{\nu} b\bar{b}$ through WW Fusion, and considers various backgrounds. Unlike previous studies, this investigation closely evaluates the effect of detector performance on the coupling uncertainty. The model-independent uncertainty on Higgs to WW coupling is found to be !!! using an optimized detector.
\end{abstract}

@@

The requirement on the precision of knowledge of Higgs Boson properties necessary to find new physics scales as $1/{\Lambda^2}$ \cite{TLEP}. For new physics at 1 TeV, per-cent sensitivity in Higgs couplings is ncecessary, while a per-mil sensitivity is necessary for multi-TeV new physics discoveries.

An $e^+e^-$ collider gives a clean and high-precision higgs factory useful for studying various higgs properties \cite{TLEP}.

>>>>

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{amsmath,amssymb}
\usepackage{feynmp}
\usepackage{url}
\usepackage{ulem}
\usepackage{multirow}
\usepackage{hyperref,color}
\renewcommand{\sfdefault}{phv}
\renewcommand{\baselinestretch}{1.2}

@@

\usepackage{booktabs,siunitx}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{ragged2e}
\newcolumntype{Y}{>{\centering\arraybackslash}X}

 \AtBeginDocument{
 \heavyrulewidth=.08em
 \lightrulewidth=.05em
 \cmidrulewidth=.03em
 \belowrulesep=.65ex
 \belowbottomsep=0pt
 \aboverulesep=.4ex
 \abovetopsep=0pt
 \cmidrulesep=\doublerulesep
 \cmidrulekern=.5em
 \defaultaddspace=.5em
}

@@

\begin{abstract}
This investigation seeks to evaluate the potential performance capabilities of the measurment of Higgs to WW coupling at the FCCee - a future $e^+e^-$ collider. The signal process used in the investigation is $e^+e^-\rig\nu\bar{\nu} b\bar{b}$ through WW Fusion, and considers various backgrounds. Unlike previous studies, this investigation closely evaluates the effect of detector performance on the coupling uncertainty. The uncertainty on the measurement of  $\sigma_{\nu\bar{\nu}H}$ x Br $(H \rig b\bar{b})$ is found to be 2.3\% at $\sqrt{s} = 350 \gev$ and 3.8\% at $\sqrt{s} = 240 \gev$, (compare to 0.6\% and 2.2\% in the TLEP paper) leading to a model-independent uncertainty on Higgs to WW coupling of 0.8\% and 1.1\%! respectively, and an uncertainty on the total higgs width of 1.1\% and 1.4\%, respectively (compare to 1.2\% and 2.4\% in the TLEP paper).
\end{abstract}

@@

To continue the search for physics beyond the standard model, precision knowledge of standard-model particles and their properties is required to measure deviations at higher energy scales. In investigating the Higgs boson, evidence for new physics at an energy scale of 1 TeV is expressed in deviations of the Higgs boson coupling to gauge bosons and fermions of up to 5\% relative to Standard Model predictions, and scales as $1/{\Lambda^2}$ \cite{tlep}. It is therefore necessary to measure Higgs boson couplings to per-cent accuracy or better to be sensitive to new physics at 1 TeV, and to per-mil accuracy or better to be sensitive to new  physics at multi-TeV.

Among the possible machines proposed for a precision study of the standard model particles, the FCC-ee (Future Circular Collider electron-positron) stands out as the tool of choice. A circular $e^+e^-$ collider gives a high-luminosity higgs factory with a clean detection environment useful for studying various higgs properties as well as Z and W bosons and the top-quark \cite{TLEP}.

Constraining the Higgs to W boson coupling ($g_\text{HWW}$) and the total Higgs boson width ($\Gamma_\text{tot}$) is a top priority.

One path for this measurement is through studying the process $e^+e^-\rig\nu\bar{\nu} b\bar{b}$. This final state occurs through two processes, Higgs-strahlung (HZ) \ref{fig:hz_feyn} where the Z decays into a neutrino pair, and WW fusion \ref{fig:hz_feyn}.

\begin{fmffile}{simple_labels}
	\begin{fmfgraph}(40,25)
		\fmfleft{i1,i2}
		\fmfright{o1,o2}
		\fmflabel{$e^-$}{i1}
		\fmflabel{$e^+$}{i2}
		\fmflabel{$h$}{o1}
		\fmflabel{$z$}{o2}
		\fmf{fermion}{i2,v1,i1}
		\fmf{fermion}{o1,v2,o2}
		\fmf{photon,label=$Z^*$}{v1,v2}
	\end{fmfgraph}
\end{fmffile}
